The `geomnet` package

### 2018-10-09 README.Rmd
website fixed

You can install `geomnet` directly from CRAN
`install.packages('geomnet')`
or from Github
`devtools::install_github("sctyner/geomnet")`
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

>>>>

You can install `geomnet` directly from CRAN
`install.packages('geomnet')`
or from Github
`devtools::install_github("sctyner/geomnet")`
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
